\MarginText{Sturdy Statistics}\NewEntry{2025--present}{Co-Founder \& CEO}

\begin{innerlist}
\item Co-founded Sturdy Statistics to help organizations make sense of unstructured data using accessible, high-quality statistical tools.
\item Helped design and implement our core technology, and developed key intellectual property.
\item Guided the company through its initial growth as we built a foundation for long-term impact.
\end{innerlist}


\MarginText{Invoca}\NewEntry{2022--2024}{Senior Principal Data Scientist}

\begin{innerlist}
\item Re-architected Invoca's machine learning codebase to enhance scalability and flexibility for both production and research use cases.
\item Mentored interns and junior scientists, supporting their career development while maintaining rapid R\&D progress.
\item Media Interview: ``Real-time conversational insights from phone call data with Mike McCourt from Invoca.'' \href{https://practicalai.fm/77}{(Practical AI \#77)}  
\end{innerlist}


\NewEntry{2020--2022}{Principal Data Scientist}

\begin{innerlist}
\item Spearheaded customer-first R\&D initiatives by identifying pain points and developing a novel natural language classifier tailored to client needs. Delivered production-ready code and submitted a supporting patent application.
\item Collaborated across product and data science leadership to plan and execute the migration of customers from the DialogTech platform following acquisition.
\item Primary inventor on three AI-focused patents:
  \begin{itemize}
    \item \textsc{\MakeTextLowercase{US 12,230,253}} - Automatic classification of phone calls
    \item \textsc{\MakeTextLowercase{US 11,429,901}} - Incorporating domain knowledge into AI models
    \item \textsc{\MakeTextLowercase{US 2024/0312451}} (pending) - Topic-based semantic search
  \end{itemize}
\end{innerlist}


\NewEntry{2019--2020}{Staff Data Scientist}

\begin{innerlist}
\item Received the President's Club award for exceptional contributions to the company.
\item Invented a Bayesian deep learning framework for natural language processing using the hierarchical Pitman-Yor process. (Featured in \href{https://www.invoca.com/press-release/invoca-releases-signal-discovery-to-give-marketers-access-to-an-untapped-source-of-first-party-customer-data}{press}, \href{https://www.invoca.com/press-release/invoca-releases-signal-discovery-to-give-marketers-access-to-an-untapped-source-of-first-party-customer-data}{blog}, and \href{https://opusresearch.net/2019/10/24/invoca-pushes-signal-discovery-for-analyzing-customer-conversations/}{industry} coverage)
\item Mentored three interns on impactful R\&D projects, with one joining the team full-time before starting a Ph.D.
\item Primary inventor on three AI-focused patents:
  \begin{itemize}
    \item \textsc{\MakeTextLowercase{US 11,115,520}} – Signal Discovery using AI Models
    \item \textsc{\MakeTextLowercase{US 11,521,601}} – Detecting Extraneous Topic Information
    \item \textsc{\MakeTextLowercase{US 11,804,216}} – Generating Training Datasets Using Discovery Models
  \end{itemize}
\end{innerlist}


\NewEntry{2018--2019}{Data Scientist}

\begin{innerlist}
\item Re-implemented a major third-party ML service in-house, reducing costs and enabling tighter integration with Invoca's platform.
\item Partnered with product, sales, and customer success teams to uncover customer pain points and rapidly prototype solutions.
\item Mentored an intern who later joined the team full-time.
\item Sole inventor on two granted/pending patents:
  \begin{itemize}
    \item \textsc{\MakeTextLowercase{US 10,719,783}} – Binary Signal Classifiers
    \item \textsc{\MakeTextLowercase{US 11,423,330}} – Performance Score Determiner
  \end{itemize}
\end{innerlist}
